\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Weronica Kovala}
\title{Lessons learned - a project managers confessions}
\author{[Weronica Kovala]}    					%Enter your name here                                

\setlength{\footskip}{7ex}
\begin{document}
\maketitle
\section{Slow is smooth and smooth is fast}
Sometimes you just want to see results, this is a natural process. This means that some solutions might be improvised just to work now. Several times during our project we had to rush some things to get them done in time for our water tests. All of these then had to be redone. If they would have been done properly some time would have been saved, however it would not have been possible to carry through the tests at that time. As a manager, it is your job to decide which is best - do the test in time or save the time it will take to redo everything properly? 
\section{Don't make assumptions}
Just because you think it is clear how things are prioritized and what should be done in what order does not mean that everyone else think the same thing. Make sure to double check that everyone is prioritizing the same way you are. 

\section{Always double check}
Just because people are doing what they should do does not mean that they do it right. Double check so that everyone understands the tasks. The risk is that someone gets the wrong idea about something. If this goes on for too long it might end in a part being unuseable when it is done. 

\section{Rules makes it possible to let go}
To avoid disasters, or at leas accidents, make sure that there are rules for how tests and other situations with possible risks or hazards should be handled. The risk is that people are stressed, tired or just eager to get started, which without rules might lead to a disaster. Or at least an underwater robot with water inside. Also make sure to note that if there are bubbles from something that is supposed to be water tight - this most definately means that there is a water leakage!

\section{Sponsoring}
If your project will need more money than you have - make sure to make it someones full time job to get sponsors. This is a time consuming business and you will not have the time to do this at the same time as managing the project. 

\section{Don't be afraid to start again}
Value all existing parts of the project, is this really a good idea? For some things, there will most certainly exist better solutions - try finding these. There is no point in trying to get a bad solution to work. \end{document}